From Macrogenres to Microgenres via Relationality

### 2023-08-05 response.tex

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
    \geometry{a4paper}
\title{Response to Memo}

\begin{document}
\maketitle
\section{Response to Editor's Letter}
The editor noted that the manuscript received a mixed response from the reviewers, with R1 being more positive and R2 and R3 more critical. The more critical reviewers were missing a substantive takeaway for the sociology of taste beyond the proposed methods. The editor's main recommendation was to ``to connect your findings more directly to Poetics (among other) papers that focus on `intra-genre' variation\ldots and culturally dissonant or `discrepant tastes' in music ---ideas often generated through discourse-based or ethnographic approaches that seem to be largely validated by your approach and findings.'' I decided to follow this last route. The last version of the paper trudged through multiple macro genres and their micro-variations in a somewhat listless way. For this version of the paper, I decided to focus on two macrogenres---Metal and Salsa---for which I could find some pointers in the scholarly literature regarding microgenre variation and then show how the link clustering approach can uncover some of the predicted variations in survey data. I think this more focused approach works better and is more effective in showcasing the validity of the proposed approach. I hope the reviewers agree.

\section{Response to R1}
This reviewer found the previous version of the manuscript to be ``incredibly exciting and smart'' and admired the ``relational thinking'' at the basis of the proposed approach. The reviewer also appreciated the broader implications of the argument and approach for social science data analysis more generally.

\subsection{Suggestions I took up}
\begin{itemize}
    \item R1 Suggested I acknowledge precursors of the proposed approach, such as Goldberg's Relational Class Analysis (RCA). I added a relevant discussion of this and other precursors in section 3.1.  
    \item R1 sagaciously pointed to the formal similarity between splitting a macrogenre into microgenre variation and the principle of ``equifinality'' and multiple ``causal recipes'' from Qualitative Comparative Analysis. I address this issue in footnote 3.  
    \item R1 also smartly suggested that I clarify the distinction between the micro-variations uncovered by the link-clustering approach and the more qualitative ones people may make using folk (or even official) classifications. I now address these issues in the concluding section. 
\end{itemize}

\subsection{Suggestions I didn't take up}
\begin{itemize}
    \item R1 suggested that I may perhaps expand on the more ``polemical'' strands of the previous version of the paper, comparing traditional methods against those that exploit the relationality inherent in most data. Since I have excised most of this discussion in this version of the paper, and since going in this direction would have taken the paper too far afield, I decided not to go in this direction. I retained some hints that most methods are affected by the microgenre critique and that adopting the techniques proposed in this paper can help across the board. 
\end{itemize}

\section{Response to R2}
R2 characterized the paper as offering ``an innovative approach to analyzing existing survey datasets on cultural tastes,'' noting that the strength of the paper lied primarily in its ``methodological contribution,'' but that ``the theoretical context and implications of this contribution could be better specified.''

\subsection{Suggestions I took up}
\begin{itemize}
    \item R2 noted that the introduction ended abruptly and that led the reader to lack context as to what the substance and main implications of the analysis that was to follow. To address this issue, I have revised the introduction to provide more context as to the substance of the approach and added a transition paragraph into the methods that provides a synoptic summary of what is to follow. 
    \item R2 suggests that I ``better motivate'' the microgenre concept. I have done this in two ways. First, the current version of the introduction develops the idea in more detail and reviews previous work that points to the concept in more substantive contexts. Second, the idea is also developed in more detail when reviewing previous work focused on the two genre case studies (sections 5.1 and 5.2), which also deploy or hint at the concept in a more substantive context. 
    \item R2 wondered how the microgenres induced from the link-clustering approach and whether the ``micro'' label even fits (e.g., why not meso), which are similar to the wonderings R1 had. As noted, I now address the issues of correspondence (maybe) and scale (relative) in the discussion section.
    \item R2 encouraged me to spell out the implications of the analysis, which they found ``rather narrow'' in the last version, particularly concerning ``suggested directions forward for key debates.'' I think that the macrogenre case studies do that effectively, and I have revised the discussion to reflect that.  
\end{itemize}

\subsection{Suggestions I didn't take up}
\begin{itemize}
    \item R2 complained about the ``lengthy'' methodological setup and suggested that I do more to outline the contribution ``up front'' as a way to obviate the need for a toy example. I tried versions of this, but it didn't work for me. I also like the toy example and think it is necessary for people without a technical background to get behind the black box of what the link-clustering is doing. So I kept it (although I removed the discussion of other methods, as noted so this section is less lengthy).  
\end{itemize}

\section{Response to R3}
R3 thought that the previous version of the paper did a ``fine job of completing what it sets out to do'' but didn't think that the paper made much of a theoretical or empirical contribution, thinking it read more like an introductory methods piece, suitable for pedagogy in a methods class. R3, like R2, was missing a more substantive takeaway that would address ``ongoing debates.'' The reviewer also complained about silly language.

I couldn't do much about the silly language (sorry!). Still, as noted, I rewrote the methods section focusing on two macrogenres selected because either debate existed in the literature or previous work suggested the existence of microgenre variations. I think the presented results address these debates head-on and show how the proposed method can shed light on them and move the discussion forward, so hopefully I did a bit to address this part of the reviewer's critique. 
\end{document}

### 2023-08-05 main.tex

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
    \geometry{a4paper}
\bibliographystyle{apalike}

\title{Discovering Focused Microgenre Communities}

\begin{document}
\maketitle
\subsubsection*{Abstract} 
Recent work in the sociology of taste has begun to grapple directly with the relational properties of traditional survey-based data using techniques inspired by network analysis. Despite the generally salutary results from this endeavor, critics rightly question the face and ecological validity of the vague macrogenre labels included in standard arts participation surveys (e.g., Classical, Rock, Rap). To deal with this issue, in this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, one that exploits the underlying relational patterns realized by the indirect connectivity structure of genres (via people) in a two-mode network. The link-clustering approach partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded and the fact that there is hidden heterogeneity within the broad labels we usually focus on. To demonstrate the validity of the approach, I contrast the application of the usual techniques to the same data, conceived in the usual ``macro" way, and after discovering hidden microgenres. The results reveal an intuitive partition of traditional macrogenres into focused microgenres, capable of separating audiences along relevant sociodemographic markers, such as education, ethnoracial identity, subjective class identification, and age/generation. 
\newpage

\section{People and Cultural Choices}
Recent work in the sociology of taste has blurred the distinction, foundational for much early work, between ``relational'' network data (codifying the relationships between people) and survey data (codifying the relationship between people and ``variables''). The basic idea is that all data, whether collected purposefully as ``network'' data collected as part of a social survey, is \textit{relational} data. The main difference is the types of entities that are related \citep{borgatti_everett97}. Any data source that can be stored in matrix form has ``modes'' (how many types of entities are related) and ``ways'' (the number of entities linked by a relation, usually two at a time). The standard network data set is ``one mode'' (we usually look at one type of entity at a time, like people, organizations, schools, countries, and the like) and two ``ways'' (people-by-people or organization-by-organization pairs). In the same way, the usual person-by-variables survey data has two modes and two ways. The relations are not people-by-people but people-by-variables. People are connected to the survey items they answer by relations of affinity, disagreement, choice, or even negatively (by not answering). Following, \citet{breiger74}, it is possible to recover person-by-person (one mode, two ways) matrices from the usual person-by-variables data matrices. People can be connected to others if they share the same values, opinions, tastes, practices, or demographics recorded as variables in the columns of the matrix.

@@

Accordingly, a spate of recent work has begun the job of theoretical translation, enriching the first-generation of work in the sociology of taste with network-flavored concepts. Accordingly, \citet{pachucki2010cultural} extend Ronald Burt's theory of structural holes for understanding how people can bridge gaps not just in one-mode person-to-person networks but in two-mode person-to-culture networks. Following this lead, \citet{lizardo14} provides a metric based on Burt's conception of network efficiency that is meant to characterize the slippery concept of ``omnivorousness" concerning genres and cultural forms people engage in. This approach goes beyond just summing or counting people's cultural engagements to consider the audience overlap between the genres themselves. Thus, the true omnivore is a person who consumes genres with low audience overlap. Other work in this same vein extends ideas related to positional equivalence in networks \citet{breiger1976social} to uncover ``blocks'' of respondents that tend to dislike the same set of genres that others like \citep{okada2017structure}. A similar approach, based on ideas of positional equivalence in networks, can be extended beyond the study of beliefs and social attitudes to identify respondents who share cultural schemas \citep{goldberg2011mapping}. \citet{lizardo18} adapts techniques first developed for the study of economic complexity in two-mode networks of geographic sites and products/technologies for the characterization of genres (e.g., popular versus niche) and audience (e.g., omnivore versus ``univore'') characteristics in survey data on cultural tastes.

@@

Thus, for DiMaggio, genres are dual entities precisely in Breiger's sense defined above. Genre categories are composed of the audiences that engage them (are subsets of the larger set of people). People, on the other hand, are related to one another (e.g., via relations of similarity, opposition, or non-overlap) by the genres they choose, and genres related to one another via overlaps (intersections) in the sets of people who choose them \citet{lizardo18}.

Like much network theorizing, this conceptualization is elegant but gets messy in the application. As \citet[149]{lena2015relational} has noted, ``[n]o ordering principle is as fundamental to culture as genre'' yet, none is also as vexed. Lena raises one issue: Sociologists have relational intuitions about genres but tend to default to musicological definitions for convenience. Thus, when it comes to considering which genres to include in a survey on cultural tastes, the tendency is to pick off-the-shelf from the menu of genre categories. The problem with these folk genre classifications is that they miss the fuzzy, overlapping ways real-world genres are organized. This leads us to treat what are, in fact, contested boundaries as if they were natural, crisp boundaries (e.g., assigning respondents who like ``Rap'' to a different taste community than those who like ``Opera."). This is the problem of \textit{overlapping boundaries among genre categories}.

The other issue has to do with the level of aggregation. For convenience’s sake, survey data must settle on a ``middle'' level of categorization so as not to tax respondents' patience (or knowledge). Thus, the standard ``lists'' of cultural genres, such as ``Pop Art,'' ``Romantic Comedy," or ``Blues.'' However, as recent work points out, people, venues, fandoms, scenes, subcultures, communities, organizations, critics, gatekeepers, and even states and other powerful institutions, make sociologically relevant distinctions within macrogenres categories \citep{hesmondhalgh2005subcultures, Holt2007, Van_Poecke2018, Hield2014-xe}. Genres may also develop and accumulate variations as they ``travel'' across production, dissemination, and consumption sites in their historical trajectory \citep{Lena2012}. These ``microgenres'' are embedded within larger macrogenres in complex ways that the standard survey approach misses.

For instance, within the Sheffield ``musicworld,'' the broad genre category of ``Folk''---one usually included in the typical survey questionnaire like the one used in this paper---can refer to at least three existing microgenres: A ``traditionalist'' one---see \citep{Lena2012}---composed mainly of late nineteenth and early twentieth English ballads documenting working-class and mining-town life, a ``scene'' genre centered on 1960s political protest and pop songs (a la Dylan) or more contemporary ``avant-garde'' genre featuring reflexive, sometimes parodic takes on the previous two, and centered on blurring performer-audience boundaries. As Hield and Crossley \citeyearpar[197]{Hield2014-xe} note, ``[t]hese and other such distinctions are not registered in\ldots surveys.''

@@

But what happens when all the data we have (as with long-standing surveys such as the Survey for Public Participation in the Arts or the General Social Survey) is at the macrogenre label? Both overlapping boundary and microgenre heterogeneity critics of traditional genre labels would say to ignore these data and collect new data that does not rely on misleading macrogenre labels. I propose another solution: {\em Exploit the inherent relationality embedded in survey data responses} \citep{goldberg2011mapping, boutyline2017belief, lizardo18}.

More specifically, my point will be that by exploiting the inherent relationality already contained in the usual survey data (when treated as two-mode network data), old data can reveal insights that pertain to the very features sociological critics of the macrogenre label concept say are missing. In particular, it is possible to use embedded sets of relations between people and genres to discover the heterogeneous microgenre communities critics say are hidden by macrogenre labels (thus, my point is that these are hidden but not necessarily absent). This approach is thus ideal for making new use of old data.

\subsection{Precursors of the Proposed Approach}
The approach proposed here builds on the core ideas of ``duality'' and ``relationality'' that have become foundational for formal approaches to measuring culture in the sociology of taste \citep{mutzel2020duality, mohr2015formal}. In this sense, I followed a path already trailed by others. For instance, Goldberg's \citeyearpar{goldberg2011mapping} {\em Relational Class Analysis} (RCA) ``classifies the people'' (in the terms developed below when reviewing standard data-analytic approaches in the sociology of taste) included a survey by partitioning a person-by-person matrix built from higher order similarities (sums of differences of differences) between each pair of person's corresponding response vector coding their stances (e.g., like, dislike, neutral) toward a set of cultural objects (e.g., genres, attitude items).

Boutyline's 
\citeyearpar{boutyline2017improving} {\em Correlational Class Analysis} (CCA) also classifies the people but this time by using the absolute value of the correlation distance between response vectors to build the person-by-person similarity matrix. Boutyline and Vaisey's {\em Belief Network Analysis} (BNA) classifies the objects people connect to (in their case, beliefs, but could also be genres) by creating a weighted object network, where the weight of the tie between two objects (attitude toward government spending and attitude toward immigration) is given by the magnitude of their correlation coefficient in the survey.

As we will see, I propose a complementary and synergistic approach with these previous efforts. More to the point, the relational identification of microgenres should be able to improve the applicability of techniques like RCA, CCA, and BNA (and related techniques) because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis and so forth), and even techniques (like Multiple Correspondence Analysis that are sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse. Thus, RCA and CCA are bound to compute relationality and correlation distances within people but have to rely on vague macrogenre labels.

The resulting evaluation logics are thus interpreted using a macrogenre lens---e.g., ``Anything but Heavy Metal'' or ``Highbrow versus Lowbrow" \citep[e.g.,][]{goldberg2011mapping, willekens2022cultural}. But what if what one group means by ``Heavy Metal" differs from what another group means by the same vague label? Are we certain that certain {\em all} types of classical music are ``opposed'' to or divergent from engagement with Country or Hip Hop? Some versions of Indie/Alt Rock are considered today as ``highbrow'' as Classical music (used to be) \citep{Van_Poecke2018}; or there may exist types of Country music that appeal to highly educated audiences and, thus, to people who might also listen to musicals? All quantitative techniques researchers use in the sociology of taste must work with the (broad) genre categories included in the survey. As such, they are powerless to deal with these (reasonable) objections.

@@

\section{Analytic Appproach}
\subsection{Data to be Used in the Study}
The empirical part of the study uses data on the musical tastes of Americans collected with Sara Skiles in the summer of 2012 \citep{lizardo_skiles15, lizardo_skiles16}. The survey was (partially) designed to replicate the General Social Survey (GSS) 1993 Culture Module. This is now a canonical data set providing the empirical basis for a variety of analyses (and reanalyses) in the sociology of taste \citep[e.g.,][]{bryson96, goldberg2011mapping, schultz2010strength, han2003unraveling, tampubolon2008revisiting, okada2017structure}.  The data were collected by an organization then called Survey Sample International (SSI), a private firm specializing in sampling, data collection, and analysis. SSI managed recruitment and participation invitation tasks to generate a panel of adults from which our working sample was drawn. Survey respondents were selected from the panel for participation based on age, gender, race, education, and geographic region to approximate a sample representative of the U.S. population ($n = 2,263$).

@@

\subsection{The Link Clustering Approach}
I propose that exploiting {\em relationality} hidden in the usual survey data collecting information on people and genres can help us make headway on the microgenre critique outlined in the preceding. As noted at the outset, this requires that we stop looking at the usual survey data that forms the bulk of empirical material in the quantitative study of taste as ``survey data'' (e.g., data collected on the characteristics of individuals in the form of ``variables''). This presumption is baked into traditional techniques (like Factor Analysis or Latent Class Analysis) that fit statistical models to such data. It is also embedded in ``relational'' techniques like Multiple Correspondence Analysis which, while not steeped in the preoccupations of standard statistical inference (although it could be), divert our attention to the indirect relations between macrogenres (or between people), usually conceptualized as distances in a social space. This kind of indirect relationality is fine and dandy. Still, as already noted in the case of RCA, CCA, and BNA, all the relationality built into MCA is powerless if what is fed {\em into} the process is the same old, limited, overextended macrogenre categories.

@@

\begin{figure}[t!]
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
\end{figure}

How does this work? As Figure~\ref{fig:link-toy1} shows, once we string out the original two-mode person-by-network in our toy example into an edge list (now containing eleven person-genre edges), where the cases are the person to genre pairs that are marked by a ``1'' in the original matrix, it is possible to ask: ``How similar is one edge to another?'' We can answer that question as follows. The similarity of one person-to-genre edge to another, when both edges point to the same genre \citep{ahn_etal10}, should be proportional to the overlap between the ``cultural ego networks'' of the two people at the tail end of the edges. As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person.

Going back to our running toy example, we are tasked with computing the similarities between $\frac{11 \times (11-1)}{2} = 55$ person-to-genre pairs. Suppose we wanted to calculate the similarity between the $P_1-G_2$ and $P_3-G_2$ person-to-genre edges in the two-mode network. In Figure~\ref{fig:link-toy1}, these two links are highlighted in yellow by the ``strung out'' edgelist and are shown in red in the corresponding bipartite subgraph shown in Figure~\ref{fig:link-toy2}. The similarity ($S$) between the two links is then given by:

@@

Where $n_+(P_1)$ is the cultural ego network of Person 1 and $n_+(P_3)$ is the cultural ego network of Person 3. The formula says that the similarity between two person-to-genre links sharing a genre, in this case, the similarity between the $P_1-G_2$ edge and the $P_3-G_2$ edge, is given by the intersection of Person 1's and Person 3's cultural ego network divided by their union (also known as Jaccard's coefficient). When the cultural ego networks of two people are the same $S=1$, when they are completely disjoint, sharing no genres, meaning the intersection is the empty set,  $S = 0$. All other cases of person-to-genre edges sharing the same genre return a number between zero and one ($0 > S < 1$).\footnote{Note that the only substantive similarities we care about are between person-to-genre edges that share the same genre but have different people attached to them at the other end. All other person-to-genre edges featuring people connected to different genres are set to zero.} In the toy example case, $P_1$ and $P_3$ consume two genres out of the four possible ones they could consume in common, resulting in an edge similarity score of $\frac{2}{4} = 0.50$.

>>>>

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage{tablefootnote}
    \geometry{a4paper}
\bibliographystyle{apalike}

\title{From Macrogenres to Microgenres via Relationality}

\begin{document}
\maketitle
\subsubsection*{Abstract} 
Recent work in the sociology of taste has begun to grapple with the relational properties of traditional survey-based data using techniques inspired by network analysis. Despite productive results from this endeavor, critics rightly question the face and ecological validity of the vague macrogenre labels included in standard arts participation surveys (e.g., Classical, Rock, Rap), which feed into these novel methods. In this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, exploiting the underlying relational patterns realized by the indirect connectivity structure of genres (via people) in a two-mode network. The link-clustering approach partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded and the fact that there is hidden heterogeneity within the broad labels we usually focus on. The results reveal an intuitive partition of traditional macrogenres into focused microgenres, capable of separating audiences along relevant sociodemographic markers, such as education, gender and ethnoracial identities, and age/generation. 
\newpage

\section{People and Cultural Choices}
Recent work in the sociology of taste has blurred the distinction, foundational for much early work, between ``relational'' network data (codifying the relationships between people) and survey data (codifying the relationship between people and ``variables''). The basic idea is that all data, whether collected purposefully as ``network'' data collected or gathered as part of a traditional social survey, is \textit{relational} data. The main difference is the types of entities that are related \citep{borgatti_everett97}. Any data source that can be stored in matrix form has ``modes'' (the types of linked entities) and ``ways'' (the number of entities linked by a relation, usually two at a time). The standard network data set is ``one mode'' (we usually look at one type of entity at a time, like people, organizations, schools, countries, and the like) and two ``ways'' (people-by-people or organization-by-organization pairs). In the same way, the usual person-by-variables survey data has two modes and two ways. The relations are not people-by-people but people-by-variables. People are connected to the survey items they answer by relations of affinity, disagreement, choice, or even negatively (by not answering). Following, \citet{breiger74}, it is possible to recover person-by-person (one mode, two ways) matrices from the usual person-by-variables data matrices. People can be connected to others if they share the same values, opinions, tastes, practices, or demographics recorded as variables in the columns of the matrix.

@@

Accordingly, a spate of recent work has begun the job of theoretical translation, enriching the first-generation of work in the sociology of taste with network-flavored concepts. For instance, \citet{pachucki2010cultural} extend Ronald Burt's theory of structural holes for understanding how people can bridge gaps not just in one-mode person-to-person networks but in two-mode person-to-culture networks. Following this lead, \citet{lizardo14} provides a metric for such holes in cultural structure based on Burt's conception of network efficiency that is meant to characterize the slippery concept of ``omnivorousness" concerning genres and cultural forms people engage in. This approach goes beyond just summing or counting people's cultural engagements to consider the audience overlap between the genres themselves. Thus, the true omnivore is a person who consumes genres with low audience overlap. Other work in this same vein extends ideas related to positional equivalence in networks \citet{breiger1976social} to uncover ``blocks'' of respondents that tend to dislike the same set of genres that others like \citep{okada2017structure}. A similar approach, based on ideas of positional equivalence in networks, can be extended beyond the study of beliefs and social attitudes to identify respondents who share cultural schemas \citep{goldberg2011mapping}. \citet{lizardo18} adapts techniques first developed for the study of economic complexity in two-mode networks of geographic sites and products/technologies \citep{hidalgo2009building} for characterizing genres (e.g., popular versus niche) and audiences (e.g., omnivore versus ``univore'') in survey data on cultural tastes.

@@

Thus, for DiMaggio, genres are dual entities precisely in Breiger's (1974) sense defined above. Genre categories are composed of the audiences that engage them (are subsets of the larger set of people). People, on the other hand, are related to one another (e.g., via relations of similarity, opposition, or non-overlap) by the genres they choose, and genres related to one another via overlaps (intersections) in the sets of people who choose them \citet{lizardo18}.

Like much network theorizing, this conceptualization is elegant but gets messy in application. As \citet[149]{lena2015relational} has noted, ``[n]o ordering principle is as fundamental to culture as genre'' yet, none is also as vexed. Lena raises one fundamental issue: Sociologists have relational intuitions about genres but tend to default to musicological definitions for convenience. Thus, when it comes to considering which genres to include in a survey on cultural tastes, the tendency is to pick off-the-shelf from the menu of genre categories. The problem with these folk genre classifications is that they miss the fuzzy, overlapping ways real-world genres are organized. This leads us to treat what are, in fact, contested boundaries as if they were natural, crisp boundaries (e.g., assigning respondents who like ``Rap'' to a different taste community than those who like ``Opera."). This is the problem of \textit{overlapping boundaries among genre categories}.

The other issue has to do with the level of aggregation. For convenience’s sake, survey data must settle on a ``middle'' level of categorization so as not to tax respondents' patience (or knowledge). Thus, the standard ``lists'' of cultural genres, such as ``Pop Art,'' ``Romantic Comedy," or ``Blues.'' However, as recent work points out, people, venues, fandoms, scenes, subcultures, communities, organizations, critics, gatekeepers, and even states and other powerful institutions, make sociologically relevant distinctions \textit{within} macrogenres categories \citep{hesmondhalgh2005subcultures, Holt2007, Van_Poecke2018, Hield2014-xe}. Genres may also develop and accumulate variations as they ``travel'' across production, dissemination, and consumption sites in their historical trajectory \citep{Lena2012}. These ``microgenres'' are embedded within larger macrogenres in complex ways that the standard survey approach misses.

For instance, within the Sheffield ``musicworld,'' the broad genre category of ``Folk''---one usually included in the typical survey questionnaire like the one used in this paper---can refer to at least three existing microgenres: A ``traditionalist'' one---see \citep{Lena2012}---composed mainly of late nineteenth and early twentieth English ballads documenting working-class and mining-town life, a ``scene'' genre centered on 1960s political protest and pop songs (a la Bob Dylan) or more contemporary ``avant-garde'' genre featuring reflexive, sometimes parodic takes on the previous two, and centered on blurring performer-audience boundaries. As Hield and Crossley \citeyearpar[197]{Hield2014-xe} note, ``[t]hese and other such distinctions are not registered in\ldots surveys.''

@@

But what happens when the data at our disposal (as with long-standing surveys such as the Survey for Public Participation in the Arts or the General Social Survey) is at the macrogenre label? Both overlapping boundary and microgenre heterogeneity critics of traditional genre labels would say to ignore these data and collect new data that does not rely on misleading macrogenre labels. I propose another solution: {\em Exploit the inherent relationality embedded in survey data responses} \citep{goldberg2011mapping, boutyline2017belief, lizardo18}. More specifically, my point will be that by exploiting the inherent relationality already contained in the usual survey data (when treated as two-mode network data), old data can reveal insights that pertain to the very features sociological critics of the macrogenre label concept say are missing. In particular, it is possible to use embedded sets of relations between people and genres to discover the heterogeneous microgenre communities critics say are hidden by macrogenre labels. This approach is thus ideal for making new use of old data while, at the same time, sidestepping some, but not all, the limitations of the microgenre critique.

\subsection{Precursors of the Proposed Approach}
The approach proposed here builds on the core ideas of ``duality'' and ``relationality'' that have become foundational for formal approaches to measuring culture in the sociology of taste \citep{mutzel2020duality, mohr2015formal}. In this sense, I followed a path already trailed by others. For instance, Goldberg's \citeyearpar{goldberg2011mapping} {\em Relational Class Analysis} (RCA) ``classifies the people''  included a survey by partitioning a person-by-person matrix built from higher order similarities (sums of differences-of-differences) between each pair of person's corresponding response vector coding their stances (e.g., like, dislike, neutral) toward a set of cultural objects (e.g., genres, attitude items). Boutyline's \citeyearpar{boutyline2017improving} {\em Correlational Class Analysis} (CCA) also classifies the people but this time by using the absolute value of the correlation distance between response vectors to build the person-by-person similarity matrix. Boutyline and Vaisey's {\em Belief Network Analysis} (BNA) classifies the objects people connect to (in their case, beliefs, but could also be genres) by creating a weighted object network, where the weight of the tie between two objects (attitude toward government spending and attitude toward immigration) is given by the magnitude of their correlation coefficient in the survey.

As we will see, I propose a complementary and synergistic approach with these previous efforts. More to the point, the relational identification of microgenres should be able to improve the applicability of techniques like RCA, CCA, and BNA (and related techniques) because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis and so forth), and even techniques like Multiple Correspondence Analysis sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse. Thus, RCA and CCA are bound to compute relationality and correlation distances within people but have to rely on vague macrogenre labels.

The resulting evaluation logics are thus interpreted using a macrogenre lens---e.g., ``Anything but Heavy Metal'' or ``Highbrow versus Lowbrow" \citep[e.g.,][]{goldberg2011mapping, willekens2022cultural}. But what if what one group means by ``Heavy Metal" differs from what another group means by the same vague label? Are we certain that certain {\em all} types of classical music are ``opposed'' to or divergent from engagement with Country or Hip Hop? Some versions of Indie/Alt Rock are considered today as ``highbrow'' as Classical music (used to be) \citep{Van_Poecke2018}; or there may exist types of Country music that appeal to highly educated audiences and, thus, to people who might also listen to musicals? All quantitative techniques researchers use in the sociology of taste must work with the (broad) genre categories included in the survey. As such, they are powerless to deal with the (reasonable) objections brought up by the microgenre dissenters.

@@

In the remainder of the paper, I introduce the link-clustering approach to eliciting microgenres using the relational information embedded in the joint choices (and avoidance) of macrogenres available in traditional survey data. I first introduce the motivation behind the method using a simple ``toy example'' and then move to the more substantive ground in two ``case studies,'' concerning two genres for which substantiated proposals exist in the literature regarding micro-variations. I show that the proposed approach extracts novel insights from survey data that help address, shed light on, and adjudicate these debates at a population level while providing novel leads to future work.

\section{Analytic Approach}
\subsection{Data to be Used in the Study}
The empirical part of the study uses data on the musical tastes of Americans collected with Sara Skiles in the summer of 2012 \citep{lizardo_skiles15, lizardo_skiles16}. The survey was (partially) designed to replicate the General Social Survey (GSS) 1993 Culture Module. This is now a canonical data set providing the empirical basis for a variety of analyses (and reanalyses) in the sociology of taste \citep[e.g.,][]{bryson96, goldberg2011mapping, schultz2010strength, han2003unraveling, tampubolon2008revisiting, okada2017structure}.  The data were collected by an organization then called Survey Sample International (SSI), a private firm specializing in sampling, data collection, and analysis. SSI managed recruitment and participation invitation tasks to generate a panel of adults from which our working sample was drawn. Survey respondents were selected from the panel for participation based on age, gender, race, education, and geographic region to approximate a sample representative of the U.S. population ($n = 2,263$).

@@

\subsection{The Link Clustering Approach}
I propose that exploiting {\em relationality} hidden in the usual survey data collecting information on people and genres can help us make headway on the microgenre critique outlined in the preceding. As noted at the outset, this requires that we stop looking at the usual survey data that forms the bulk of empirical material in the quantitative study of taste as ``survey data'' (e.g., data collected on the characteristics of individuals in the form of ``variables''). As noted, this assumption is baked into traditional techniques (like Factor Analysis or Latent Class Analysis) that fit statistical models to such data. But it is also embedded in ``relational'' techniques like Multiple Correspondence Analysis which, while not steeped in the preoccupations of standard statistical inference (although they could be), divert our attention to the indirect relations between macrogenres (or between people), usually conceptualized as distances in a social space \citep{flemmen_etal18}. This kind of indirect relationality is fine and dandy. Still, as already noted in the case of RCA, CCA, and BNA, all the relationality built into MCA is powerless if what is fed {\em into} the process is the same old, limited, overextended macrogenre categories.

@@

\begin{figure}[t!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
\end{figure}

How does this work? As Figure~\ref{fig:link-toy1} shows, once we string out the original two-mode person-by-network in our toy example into an edge list (now containing eleven person-genre edges), where the cases are the person to genre pairs that are marked by a ``1'' in the original matrix, it is possible to ask: ``How similar is one edge to another?'' We can answer that question as follows. The similarity of one person-to-genre edge to another, when both edges point to the same genre \citep{ahn_etal10}, should be proportional to the overlap between the ``cultural ego networks'' of the two people at the tail end of the edges. As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person, where $k$ is the total number of genres chosen (``omnivorousness by volume'').

Going back to our running toy example, we are tasked with computing the similarities between $\frac{11 \times (11-1)}{2} = 55$ person-to-genre pairs. Suppose we wanted to calculate the similarity between the $P_1-G_2$ and $P_3-G_2$ person-to-genre edges in the two-mode network. In Figure~\ref{fig:link-toy1}, these two links are highlighted in yellow by the ``strung out'' edgelist and are shown in red in the corresponding bipartite subgraph shown in Figure~\ref{fig:link-toy2}. The usual Jaccard distance then gives the similarity ($S$) between the two links:

@@

Where $n_+(P_1)$ is the cultural ego network of Person 1 and $n_+(P_3)$ is the cultural ego network of Person 3. The formula says that the similarity between two person-to-genre links sharing a genre, in this case, the similarity between the $P_1-G_2$ edge and the $P_3-G_2$ edge, is given by the intersection of Person 1's and Person 3's cultural ego network divided by their union. When the cultural ego networks of two people are the same $S=1$ when they are completely disjoint $S = 0$. All other cases of person-to-genre edges sharing the same genre return a number between zero and one ($0 > S < 1$).\footnote{Note that the only substantive similarities we care about are between person-to-genre edges that share the same genre but have different people attached to them at the other end. All other person-to-genre edges similarities featuring people connected to different genres are set to zero.} In the toy example case, $P_1$ and $P_3$ consume two genres out of the four possible ones they could consume in common, resulting in an edge similarity score of $\frac{2}{4} = 0.50$.

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
        \caption{Edge similarity matrix from toy example.}
        \label{tab:toy-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
        \caption{Edge distance matrix from toy example.}
        \label{tab:toy-dis}
    \end{subfigure}
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy.png}
        \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
        \label{fig:link-toy}
    \end{subfigure}
    \caption{Toy illustration of how the link clustering approach works.}
    \label{fig:link-toy-ex}
 \end{figure}
